\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
The past two years at the Australian National University have been an invaluable experience for me. When I started my Master of Machine Learning and Computer Vision at the beginning of 2019, I could barely understand lectures, knew little about the country, and had never heard of the term "convex optimization". It is unbelievable that I have been doing a research project on this topic for a whole year. ANU has the top tier research group in this realm and how honored I am to be a postgraduate student here. 
\par First and foremost, I would like to express my deep and sincere gratitude to my supervisor, Stephen Gould. I knew Stephen before the admission of the program and how privileged I am to work and learn with one of the most brilliant minds in our field. He always has an insightful and high-level view on this topic. More importantly, Stephen is extremely kind and patient as he is always willing to discuss and share ideas with us during the weekly meetings. Although sometimes I stuck in some problems that he has given me constructive suggestions. 
\par I would like to thank Dylan Campbell and Miaomiao Liu -- another two giants of the Australian Centre for Robotic Vision -- for offering me supervision and being my second examiner on my thesis. Dylan is always enthusiastic and knowledgeable, and his ideas and works inspire me a lot in my research. Although I have not worked with Miaomiao before, her works in the computer vision area are very impressive, which makes me work hard to complete this research. I want to thank her for her time examining my thesis seminar. 
\par During my research, I have very fun collaboration and discussion with collaborators in our research group: Jiteng Ma, Jingyi Zhang, Yuchong Yao, Ruikai Cui, and Wenbo Du. Although we almost never meet in person due to the COVID-19, we still share many ideas related to our research through the social network. I greatly enjoyed the teamwork with them.
\par Outside the research group, I am very lucky to be surrounded by many great friends. Yao Liu, Ce Wang and Nuocheng Tian -- We almost study together every single day during the academic year, even on the public holidays. I am impressed by their insightful ideas and I really appreciate the brainstorming with them. Mingrui Zhao -- As my closest partner, a charming Engineering \& Mathematics double-degree undergraduate student and my math "teacher", he always encourages me to pursue my academic ambition and I learned a lot from him. 
\par I thank my parents: Shiwu Wang and Hongyin Shen. As traditional Asian parents, they never restrict my life planning, and always encourage me to fulfill my dream. I hope that they will a little proud of me. 